{{< var titll >}}

### 2024-07-09 presentation.qmd
beftoc

# {{< var sec1.nmn >}}
## {{< var sec1.un1 >}}
## {{< var sec1.un2 >}}
## {{< var sec1.un3 >}}
## {{< var sec1.un4 >}}
## {{< var sec1.un5 >}}
## {{< var sec1.un6 >}}
## {{< var sec1.un7 >}}

# {{< var sec2.nmn >}}
## {{< var sec2.un1 >}}
## {{< var sec2.un2 >}}
## {{< var sec2.un3 >}}
## {{< var sec2.un4 >}}
## {{< var sec2.un4 >}}

# {{< var sec3.nmn >}}
## {{< var sec3.un1 >}}
## {{< var sec3.un2 >}}

# {{< var sec6.nmn >}}
## {{< var sec6.un1 >}}
## {{< var sec6.un2 >}}
## {{< var sec6.un3 >}}
## {{< var sec6.un4 >}}

# {{< var sec7.nmn >}}
## {{< var sec7.un1 >}}

## `r metad$toc$sec1$unm[1]`

lego_hux_imp_ii
```
::::

# `r metad$toc$sec1$nmn`

Ed. Solomon

## `r metad$toc$sec1$unm[1]`

- Two candidates: A, B
- County with three precincts: 1, 2, 3
- Two modes of voting
  - Number of ballots mode 1: S, T
  - Number of ballots mode 2: U, V

@@

lego_hux_imp_ii
```
::::

## `r metad$toc$sec1$unm[2]`

```{r, echo=F}
lego_hux_nor <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
  set_background_color(1, 1:2, "black") %>% 
  set_background_color(2, 1:2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_nor %>% set_caption("")
```

@@

## `r metad$toc$sec1$unm[3]`

```{r, echo=F}
lego_hux_imp <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
  set_background_color(1:2, 1, "black") %>% 
  set_background_color(1:2, 2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_imp %>% set_caption("")
```

@@

## `r metad$toc$sec1$unm[4]`

```{r, echo=F}
lego_hux_opo <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
  set_background_color(c(1),c(1), "black") %>% 
  set_background_color(c(2),c(2), "black") %>% 
  set_background_color(c(1),c(2), "grey") %>% 
  set_background_color(c(2),c(1), "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_opo %>% set_caption("")
```

@@

## `r metad$toc$sec1$unm[5]`

@@

## `r metad$toc$sec1$unm[6]`

@@

## `r metad$toc$sec1$unm[7]`

@@

# `r metad$toc$sec2$nmn`

## `r metad$toc$sec2$unm[1]`

- We have identified three ways of counting
  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
-  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
  -  We are free to *predetermine* **3** of them
  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
  -  Selecting **3** parameters from a set of **5** implies **10** different combinations

## `r metad$toc$sec2$unm[2]`

::: {.callout-caution collapse="true"}
**20 laws and 40 isometris**

@@

## `r metad$toc$sec2$unm[3]`

@@

## `r metad$toc$sec2$unm[4]`

@@

::: {.column width="50%"}
Non-rigged election using standard form
```{r}
app_n_out[[4]] 
```

@@

Rigged election using standard form
```{r}
app_ex1_out[[4]] 
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
\end{equation*}

Election outome 
```{r, echo=F}
#pri_int_ex1
#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
mean(app_ex1_cou$rdfc$alpha)
```

@@

$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$

Election outome
```{r, echo=F}
#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
pos_int_ex1
```

@@

@@

Non-rigged election using standard form
```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
app_n_out[[4]] 
```

Rigged election using standard form
```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
app_ex1_out[[4]] 
```
:::

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex3)),3))`$
\end{equation*}

Election outome
```{r, echo=F}
#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pri_int_ex3))),c(0,1))
```

$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pos_int_ex3)),3))`$

Election outome
```{r, echo=F}
#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pos_int_ex3))),c(0,1))
```

@@

## `r metad$toc$sec2$unm[5]`

- Specify a loss function
  - $\sum_{p=1}^{P}(\alpha_p-\overline{\alpha})^2$
- $M(,)=$x+y$
  - Use: Linear, quadratic, cubic or quartic (all have analytical solutions)
  - Also: Euler rotation
- System approach Demands mulitvariate Manifold Equations
  - Univariate manifold Equation
  - Multivariate Manifold Equations
- Constrain on implementation
  - Flipping votes on one mode
  - Vote registration until upper limit

```{r, echo=F, out.width="80%", fig.cap=""}
bI <- paste0(rprojroot::find_rstudio_root_file(),'pngs/loss_5_conditions.png')
knitr::include_graphics(bI)
```

# `r metad$toc$sec3$nmn`

## `r metad$toc$sec3$unm[1]`

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_n_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_n_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_n_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_n_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_n_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_n_out[['resp']]
```

## `r metad$toc$sec3$unm[2]`

**Example 1: Normal form**

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_ex1_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_ex1_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['resp']]
```

**Example 2: applying hybrid form**

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_ex2_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_ex2_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['resp']]
```

**Example 3: applying opposition form**

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_ex3_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_ex3_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['resp']]
```

# `r metad$toc$sec4$nmn` {#litrev}

```{r, echo=FALSE, out.width="20%", fig.cap=""}
p1 <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/ss.png')
knitr::include_graphics(c(p1))
```

`r #Citet(bib, "delfino2011analysis")`

> Abstract: On August 15th, **2004**, Venezuelans had the opportunity to vote
in a Presidential Recall Referendum **to decide whether or not President Hugo
Chávez should be removed from office.** **The process was largely computer-
ized using a touch-screen system.** In general the ballots were not manually
counted. The significance of the high linear correlation (0.99) between the
number of requesting signatures for the recall petition and the number of op-
position votes in computerized centers is analyzed. The same-day audit was
found to be not only ineffective but a source of suspicion...

::: aside
[Link to Youtube-video](https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s)
:::

- Venezuela referendum to recall President Hugo Chávez (2004)
	- Mode 1: Computerized Voting Centers
	- Mode 2: Manuel Voting Centers

> HYPOTHESIS: **In computerized centers**, official **results were forced to follow a linear relationship** with respect to the number of signatures.

```{r, echo=FALSE, out.width="85%", fig.cap=""}
p3 <- paste0(rprojroot::find_rstudio_root_file(),'pngs/manifold.png')
knitr::include_graphics(c(p3))
```

# `r metad$toc$sec5$nmn` {#proced}

# `r metad$toc$sec5$unm[1]`

@@

[Application 3: Rigged election analyzer]({{< var shn3 >}})

# `r metad$toc$sec6$nmn`

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="1")
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
---

# `r metad$toc$sec7$nmn`

[Application 4: Restoration of a rigged election]({{< var shn4 >}})

# `r metad$toc$sec8$nmn`

@@

- Condition on that $R^2$ falls within the critical region.
  - Normal form
```{r, echo=F, out.width="40%", fig.cap=""}
pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2n.png')
knitr::include_graphics(c(pr2n))
```

 - Hybrid form
```{r, echo=F, out.width="40%", fig.cap=""}
pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2h.png')
knitr::include_graphics(c(pr2h))
```

@@

```{r, echo=F, warning=F, message=F}
kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

# `r metad$toc$sec9$nmn`

>>>>

# {{< var sec1.nmn >}}
## {{< var sec1.un1 >}}
- Two candidates: A, B
- County with three precincts: 1, 2, 3
- Two modes of voting
  - Number of ballots mode 1: S, T
  - Number of ballots mode 2: U, V

@@

lego_hux_imp_ii
```
::::
## {{< var sec1.un2 >}}
```{r, echo=F}
lego_hux_nor <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
  set_background_color(1, 1:2, "black") %>% 
  set_background_color(2, 1:2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_nor %>% set_caption("")
```

@@

## {{< var sec1.un3 >}}
```{r, echo=F}
lego_hux_imp <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
  set_background_color(1:2, 1, "black") %>% 
  set_background_color(1:2, 2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_imp %>% set_caption("")
```

@@

## {{< var sec1.un4 >}}
```{r, echo=F}
lego_hux_opo <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
  set_background_color(c(1),c(1), "black") %>% 
  set_background_color(c(2),c(2), "black") %>% 
  set_background_color(c(1),c(2), "grey") %>% 
  set_background_color(c(2),c(1), "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_opo %>% set_caption("")
```

@@

## {{< var sec1.un5 >}}

@@

## {{< var sec1.un6 >}}

@@

## {{< var sec1.un7 >}}

@@

# {{< var sec2.nmn >}}
## {{< var sec2.un1 >}}
- We have identified three ways of counting
  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
-  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
  -  We are free to *predetermine* **3** of them
  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
  -  Selecting **3** parameters from a set of **5** implies **10** different combinations

## {{< var sec2.un2 >}}
::: {.callout-caution collapse="true"}
**20 laws and 40 isometris**

@@

:::
## {{< var sec2.un3 >}}

@@

## {{< var sec2.un4 >}}

@@

::: {.column width="50%"}
Non-rigged election using standard form
```{r}
#app_n_out[[4]] 
```

@@

Rigged election using standard form
```{r}
#app_ex1_out[[4]] 
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
\end{equation*}

Election outome 
```{r, echo=F}
#pri_int_ex1
#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
#mean(app_ex1_cou$rdfc$alpha)
```

@@

$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$

Election outome
```{r, echo=F}
#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
#pos_int_ex1
```

@@

# {{< var sec3.nmn >}}

## {{< var sec3.un1 >}}

## {{< var sec3.un2 >}}

@@

@@

@@

# {{< var sec6.nmn >}}

@@

## {{< var sec6.un1 >}}
## {{< var sec6.un2 >}}
## {{< var sec6.un3 >}}
## {{< var sec6.un4 >}}

# {{< var sec7.nmn >}}

## {{< var sec7.un1 >}}

@@

@@
